%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{121212}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Jessica Tagudar}{}

\position{Research Administration Graduate Assistant}
\address{Grand Rapids, Michigan}

\mobile{269-408-6153}
\email{\href{mailto:tagudarjessica@gmail.com}{\nolinkurl{tagudarjessica@gmail.com}}}
\github{tagudarj}
\linkedin{jessica-tagudar-a10938179}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {November, 2020}
    {Jessica Tagudar~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{BS in Allied Health Sciences}{Grand Valley State University}{Allendale, MI}{Aug. 2017 - Apr. 2020}{\begin{cvitems}
\item Major: Allied Health Sciences; Minor: Applied Statistics
\item Overall GPA: 3.4
\item Applied Statistics GPA: 3.9
\item Dean’s List: 2019, 2020
\item Related Coursework: Statistical Quality Control, Intermediate Applied Statistics, Design of Experiments, Introduction to Biostatistics, Regression Analysis, Statistical Computing, Introduction to Health Care Research
\end{cvitems}}
    \cventry{MS in Biostatistics}{Grand Valley State University}{Grand Rapids, MI}{Aug. 2020 - Present}{\begin{cvitems}
\item Expected Graduation: April 2022
\item Related Coursework: R Programming, Bioinformatics, Applied Statistics for Health Professions
\item Interests: Biostatistics, Data Analytics, Research, Epidemiology
\end{cvitems}}
\end{cventries}

\hypertarget{relevant-skills}{%
\section{Relevant Skills}\label{relevant-skills}}

\footnotesize

I developed a variety of skills through coursework and work experience.

\begin{cvhonors}
    \cvhonor{}{SAS}{ }{ }
    \cvhonor{}{R Studio}{ }{ }
    \cvhonor{}{SPSS}{ }{ }
    \cvhonor{}{JMP Pro 14}{ }{ }
    \cvhonor{}{Proficient in Microsoft programs, specifically Excel tools such as Pivot Tables}{ }{ }
    \cvhonor{}{Data collection and data transferring to/from various software}{ }{ }
    \cvhonor{}{Data software such as Cayuse and Streamlyne}{ }{ }
    \cvhonor{}{Phlebotomy Technician Certified}{ }{ }
\end{cvhonors}

\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\begin{cventries}
    \cventry{Resesarch Administrtion Graduate Assistant}{Center for Scholarly and Creative Excellence - GVSU}{Allendale, MI}{Aug. 2020 - Present}{\begin{cvitems}
\item COVID-19 Research
\item Managing COVID-19 Testing Facility
\item Assist with Office of Sponsored Programs by monitoring contracts and other duties
\end{cvitems}}
    \cventry{Resesarch Administrtion Student Assistant}{Center for Scholarly and Creative Excellence - GVSU}{Allendale, MI}{Nov. 2018 - Apr. 2020}{\begin{cvitems}
\item Collected and converted data to and from various databases
\item Data analyzing and data cleaning
\item Prepared the company for a new software launch by organizing research projects from 2011 to 2020
\item Ensured that finished research projects contain all of their necessary documents to secure their completion – such as budget forms and fully executed contracts
\item Attended conference calls to stay on track with other companies for the launch of our new software
\item Prepared learning modules directed toward faculty and staff to learn about the new software
\end{cvitems}}
    \cventry{Data Analytics Intern}{Fifth Wheel Freight}{Kentwood, MI}{May 2019 - Aug. 2019}{\begin{cvitems}
\item Interpreted data, analyze results using statistical techniques and provide ongoing reports 
\item Developed and implement databases, data collection systems, data analytics and other strategies that optimize statistical efficiency and quality
\item Identified, analyzed, and interpreted trends or patterns in complex data sets
\item Filtered and “cleaned” data by reviewing computer reports, printouts, and performance indicators to locate and correct code problems
\item Worked with management to prioritize business and information needs
\item Located and defined new process improvement opportunities
\end{cvitems}}
    \cventry{Nurse Technician}{Butterworth Hospital - Spectrum}{Grand Rapids, MI}{Sep. 2018 - Nov. 2018}{\begin{cvitems}
\item Obtained vital signs and reported any abnormalities or changes in patients’ condition and behavior
\item Assessed patients with daily activities and providing dietary and hygienic care
\end{cvitems}}
\end{cventries}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\footnotesize

My research experience contains a personal project and an assisted
project.

\begin{cventries}
    \cventry{Primary Researcher - COVID-19 Predictive Data Analysis}{Grand Valley State University}{Allendale, MI}{Oct. 2020 - Present}{\begin{cvitems}
\item Objective: To use predictive analytic models to create a risk forecast of COVID-19 for GVSU, using test result data from Trident Labs.
\item Visualizations are created using R Studio.
\end{cvitems}}
    \cventry{Research Assistant - FEV 1.0 and Lung Capacity in Band Students (by Dr. Deborah Lown and Trenton Dalm, GVSU student)}{Grand Valley State University}{Allendale, MI}{June 2019 - Apr. 2020}{\begin{cvitems}
\item Objective: To test the effectiveness of the pulmonary exercises taught by Breathing Gym on functional lung capacity and FEV 1.0 in Grand Valley State University marching band students.
\item My responsibilities included the following: Assisted with data collection using spirometers and weight/height measuring tools, analyzed and organized data to find trends over the semester, provided insight on conclusions
\end{cvitems}}
\end{cventries}

\hypertarget{awards-achievements}{%
\section{Awards \& Achievements}\label{awards-achievements}}

\hypertarget{scholarships}{%
\subsection{Scholarships}\label{scholarships}}

\begin{cvhonors}
    \cvhonor{}{GV Laker Scholarship}{GVSU}{2017-2020}
    \cvhonor{}{Statistics Book Scholarship}{GVSU - Statistics Department}{2019 \& 2020}
    \cvhonor{}{Believe in Yourself Scholarship}{SJPS Foundation}{2017}
\end{cvhonors}

\hypertarget{citation}{%
\section{Citation}\label{citation}}

\textbf{Citation}: This resume was created by using this
\href{https://github.com/mitchelloharawild/CV.git}{\textbf{Curriculum
Vitae Github Repository Link}} as a source.

\end{document}
