---
name: Jessica Tagudar
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: Allied Health Sciences, BS
position: Research Administration Graduate Assistant
address: Grand Rapids, Michigan
phone: 269-408-6153
email: tagudarjessica@gmail.com
github: tagudarj
linkedin: jessica-tagudar-a10938179
headcolor: "121212"
output: 
    vitae::awesomecv:
      keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education
```{r education}
tribble(
  ~ degree, ~ school, ~ location, ~ dates, ~ details,
  "BS in Allied Health Sciences", "Grand Valley State University", "Allendale, MI", "Aug. 2017 - Apr. 2020", "Major: Allied Health Sciences; Minor: Applied Statistics",
  "BS in Allied Health Sciences", "Grand Valley State University", "Allendale, MI", "Aug. 2017 - Apr. 2020", "Overall GPA: 3.4",
  "BS in Allied Health Sciences", "Grand Valley State University", "Allendale, MI", "Aug. 2017 - Apr. 2020", "Applied Statistics GPA: 3.9",
  "BS in Allied Health Sciences", "Grand Valley State University", "Allendale, MI", "Aug. 2017 - Apr. 2020", "Dean’s List: 2019, 2020",
  "BS in Allied Health Sciences", "Grand Valley State University", "Allendale, MI", "Aug. 2017 - Apr. 2020", "Related Coursework: Statistical Quality Control, Intermediate Applied Statistics, Design of Experiments, Introduction to Biostatistics, Regression Analysis, Statistical Computing, Introduction to Health Care Research",
  "MS in Biostatistics", "Grand Valley State University", "Grand Rapids, MI", "Aug. 2020 - Present", "Expected Graduation: April 2022",
  "MS in Biostatistics", "Grand Valley State University", "Grand Rapids, MI", "Aug. 2020 - Present", "Related Coursework: R Programming, Bioinformatics, Applied Statistics for Health Professions",
  "MS in Biostatistics", "Grand Valley State University", "Grand Rapids, MI", "Aug. 2020 - Present", "Interests: Biostatistics, Data Analytics, Research, Epidemiology"
) %>% 
  detailed_entries(degree, dates, school, location, details)
```

# Relevant Skills

\footnotesize
I developed a variety of skills through coursework and work experience.


```{r skills}
tribble(
  ~ skill, ~space, ~space2,
  "SAS", " ", " ",
  "R Studio", " ", " ",
  "SPSS", " ", " ", 
  "JMP Pro 14", " ", " ",
  "Proficient in Microsoft programs, specifically Excel tools such as Pivot Tables", " ", " ",
  "Data collection and data transferring to/from various software", " ", " ",
  "Data software such as Cayuse and Streamlyne", " ", " ",
  "Phlebotomy Technician Certified", " ", " ",
) %>% 
  brief_entries(skill, space, space2)
```

# Work Experience

```{r work}
tribble(
  ~ job, ~ company, ~ location, ~ dates, ~ details,
  "Resesarch Administrtion Graduate Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Aug. 2020 - Present", "COVID-19 Research",
  "Resesarch Administrtion Graduate Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Aug. 2020 - Present", "Managing COVID-19 Testing Facility",
  "Resesarch Administrtion Graduate Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Aug. 2020 - Present", "Assist with Office of Sponsored Programs by monitoring contracts and other duties",
  "Resesarch Administrtion Student Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Nov. 2018 - Apr. 2020", "Collected and converted data to and from various databases",
  "Resesarch Administrtion Student Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Nov. 2018 - Apr. 2020", "Data analyzing and data cleaning",
  "Resesarch Administrtion Student Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Nov. 2018 - Apr. 2020", "Prepared the company for a new software launch by organizing research projects from 2011 to 2020",
  "Resesarch Administrtion Student Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Nov. 2018 - Apr. 2020", "Ensured that finished research projects contain all of their necessary documents to secure their completion – such as budget forms and fully executed contracts",
  "Resesarch Administrtion Student Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Nov. 2018 - Apr. 2020", "Attended conference calls to stay on track with other companies for the launch of our new software",
  "Resesarch Administrtion Student Assistant", "Center for Scholarly and Creative Excellence - GVSU", "Allendale, MI", "Nov. 2018 - Apr. 2020", "Prepared learning modules directed toward faculty and staff to learn about the new software",
  "Data Analytics Intern", "Fifth Wheel Freight", "Kentwood, MI", "May 2019 - Aug. 2019", "Interpreted data, analyze results using statistical techniques and provide ongoing reports ",
   "Data Analytics Intern", "Fifth Wheel Freight", "Kentwood, MI", "May 2019 - Aug. 2019", "Developed and implement databases, data collection systems, data analytics and other strategies that optimize statistical efficiency and quality",
   "Data Analytics Intern", "Fifth Wheel Freight", "Kentwood, MI", "May 2019 - Aug. 2019", "Identified, analyzed, and interpreted trends or patterns in complex data sets",
   "Data Analytics Intern", "Fifth Wheel Freight", "Kentwood, MI", "May 2019 - Aug. 2019", "Filtered and “cleaned” data by reviewing computer reports, printouts, and performance indicators to locate and correct code problems",
   "Data Analytics Intern", "Fifth Wheel Freight", "Kentwood, MI", "May 2019 - Aug. 2019", "Worked with management to prioritize business and information needs",
   "Data Analytics Intern", "Fifth Wheel Freight", "Kentwood, MI", "May 2019 - Aug. 2019", "Located and defined new process improvement opportunities",
  "Nurse Technician", "Butterworth Hospital - Spectrum", "Grand Rapids, MI", "Sep. 2018 - Nov. 2018", "Obtained vital signs and reported any abnormalities or changes in patients’ condition and behavior",
   "Nurse Technician", "Butterworth Hospital - Spectrum", "Grand Rapids, MI", "Sep. 2018 - Nov. 2018", "Assessed patients with daily activities and providing dietary and hygienic care",
) %>% 
  detailed_entries(job, dates, company, location, details)
```

# Research Experience

\footnotesize
My research experience contains a personal project and an assisted project.


```{r research}
tribble(
  ~ role, ~ school, ~ location, ~ dates, ~ details,
  "Primary Researcher - COVID-19 Predictive Data Analysis", "Grand Valley State University", "Allendale, MI", "Oct. 2020 - Present", "Objective: To use predictive analytic models to create a risk forecast of COVID-19 for GVSU, using test result data from Trident Labs.",
  "Primary Researcher - COVID-19 Predictive Data Analysis", "Grand Valley State University", "Allendale, MI", "Oct. 2020 - Present", "Visualizations are created using R Studio.",
  "Research Assistant - FEV 1.0 and Lung Capacity in Band Students (by Dr. Deborah Lown and Trenton Dalm, GVSU student)", "Grand Valley State University", "Allendale, MI", "June 2019 - Apr. 2020", "Objective: To test the effectiveness of the pulmonary exercises taught by Breathing Gym on functional lung capacity and FEV 1.0 in Grand Valley State University marching band students.",
    "Research Assistant - FEV 1.0 and Lung Capacity in Band Students (by Dr. Deborah Lown and Trenton Dalm, GVSU student)", "Grand Valley State University", "Allendale, MI", "June 2019 - Apr. 2020", "My responsibilities included the following: Assisted with data collection using spirometers and weight/height measuring tools, analyzed and organized data to find trends over the semester, provided insight on conclusions",
) %>% 
  detailed_entries(role, dates, school, location, details)
```


# Awards & Achievements
## Scholarships 
```{r scholarships}
tribble( 
~ scholarship, ~ from, ~ year, 
"GV Laker Scholarship", "GVSU", "2017-2020", 
"Statistics Book Scholarship", "GVSU - Statistics Department", "2019 & 2020", 
"Believe in Yourself Scholarship", "SJPS Foundation", "2017"
) %>%
brief_entries(scholarship, year, from) 
``` 

# Citation
**Citation**: This resume was created by using this [**Curriculum Vitae Github Repository Link**](https://github.com/mitchelloharawild/CV.git) as a source.
